\section{Cooperation and Game Theory}
\subsection{Stag Hunt Game and the Evolution of Cooperation}

The stag hunt game is a story that became a game. 
The story has first appeared in its original form in Rousseau's 
\emph{`A Discourse on Inequality'}. 

It describes the situation where several hunters are after a stag. 
In order to successfully hunt a stag the whole group should cooperate and stay faithful to its post. 
However, if a hare happens to pass by then it is possible for one of the hunters to betray the 
others and hunt the hare alone. 
The consequence of this betrayal would be that the rest of the group will starve.

The above description is usually formalised in a game played by two players. 
They can catch a stag if and only if they cooperate, but each one can catch a hare separately if 
this hunter decides to hunt alone. 
Therefore, this game models an environment where individuals can maximise their welfare 
by cooperating but doing so entails some risk. 
The risk is due to the uncertainty introduced by not knowing the opponent's intention. 
If one of them decides to cooperate and the other one decides to defect then the former loses.

The use of the stag hunt game as a model of evolution of cooperation reveals an interesting 
paradox. 
All the efforts to date, that used the stag hunt game as the model of cooperation, have failed 
to show that a non-cooperative society can evolve into a cooperative one. 
Although, the players have higher benefit from cooperating, they tend to choose the risk 
dominant strategy which is to defect. 
Skyrms in his book 
\emph{`The stag hunt and the evolution of social structure'}
 provides a possible 
explanation for this phenomenon. 
The hare hunters can only become stag hunters if they change their beliefs about what their opponent will do. 
Classic game theory fails to capture this concept because each participant makes rational 
choices and the rational choice is to always try to improve your own satisfaction. 
In order to overcome this problem and be able to use the stag hunt game as an evolutionary 
model one must abandon the idea of rational players and consider the players as socially 
rational. 
Social rationality differs from common rationality in two aspects. 
A player is not confined to narrow self-interest and its decisions seek a “good enough” 
solution rather than a strict optimisation of its own benefit. 
In the next section we describe some basic agent strategies and how these strategies in 
combination with the concept of trust can lead to socially rational agents.

\subsection{Agent Strategies and Socially Rational Agents}
Initially an agent is assigned a type. 
The type defines the strategy this agent will follow when goes hunting. 
The strategies used in our simulations are adopted from the strategies implemented for 
Axelrod's tournament in 1980. 
There are four basic strategies:

\begin{itemize}
\item \textbf{Always defect}: An agent always chooses to defect (hunt hare) no matter what its 
opponent does.
\item \textbf{Always cooperate}: An agent always chooses to cooperate (hunts stags) no matter 
what its opponent does.
\item \textbf{Tit-for-tat}:  A tit-for-tat agent chooses to cooperate in the first iteration of the game. 
If the opponent defects then the agent loses but in the next iteration the agent choose to 
follow the strategy of its opponent in the previous round. 
So a simple algorithm for this strategy is:

\textbf{
	If t=1 then cooperate
	If t>1 then do what your opponent did in t-1
	where t is the number of rounds passed .
}

\item \textbf{Random}: This strategy ignores what the opponent has done in previous rounds 
and selects either defect or cooperate at random.

\end{itemize}

The problem with these strategies is that they are static with the only exception being the 
tit-for-tat strategy. 
These strategies do not allow any flexibility of an agent's beliefs. 
This is what causes the paradox we explained above. 
Therefore, we must force an agent to act socially rational and not just rationally.
We tried to tackle this problem by introducing the notion of trust among agents. 
Depending on how an interaction between two agents ended up the agents can increase 
or decrease their trust for another agent. 
Therefore an agent's decision depends not only on its assigned type but also on the 
information it has about its opponent. 
An agent receives information either through its own experience or by asking other agents 
for advice. 
This fact enables agents to change their beliefs about what their opponents will choose to do. 
 This flexibility in beliefs is the main reason why cooperation can emerge in our simulations.\cite{stag_hunt_evo, stag_hunt_struct}



