\subsection{Randomised Politics}

The main simulation base that we examined revolved around the formation of
groups in the stag hunt games, without some of the more complicated features
of the agents, loans, or other games between the groups.

Due to the lack of unit testing as a control mechanism, which will be 
discussed later, repeated runs of thes simualtions highlighted most of the
bugs in the code. These became apparent in strange correleations and
homogenity in the results which you would not expect with the wide range of
initial consitions.
Most of these issues were later shown to either be major programming errors
or biases, rather than emergent behaviours.

\subsubsection{Parameters and Execution}

These simulations, of which the code can be seen in excerpt \ref{CLIPolitics}
on page \pageref{CLIPolitics}, are homogenous except for the random seed.
Each one simulates 200 basic agents, 50 of each of the four core agent
strategies.
They are each allocated 20 food, and set to cosume 2 per turn - the same amount
as supplied by a rabbit in the simulation.
Stags, on the other hand, are set to supply 10 food, creating A 250\% bonus
for co-operation.

The social and economic beliefs are the first thign to be set by the random
seed - a Random class is created on the simulations random seed, which is
used to generate the pseudo-random position of all the agents.
The same random seed is ued to create the Random number generators of the
Participants in the simulation.
This random generator affects all of the pseudo-random actions that the
Participants model as probabilistic choices, such that the actions of the
Participants, as well as their initial conditions, are not exactly the same
for each of the simulations.

The simulations were run using build 11f76d\footnote{
\url{https://github.com/javajawa/ISEGameOfLife/commit/11f76d47fb27d479519d906b7b6ff97307530115}
}, and were run on the Department of Computing's high throughput computing
network, powered by Condor\footnote{
  with thanks to CSG, including David McBride
}.
A total of 250 simualtions were scheduled, with some hitting database timeout
errors due the over-parallelisation caused by the avaialblility of Condor
hosts, leaving 218 simulations, consisting of 833 rounds (5000 cycles) each.

\subsubsection{Analysis}

The results of the runs on build 11f76d were uploaded to a database hosted in
the student union\footnote{
  The server was `Corvette', Imperial College Science Fiction Society's 
  (\url{icsf.org.uk}) databae server.
  Used with kind permission.
}

