\chapter{Conclusion}

Throughout the project, we have been attempting to simulate interesting
and relevant models real world behaviour, in an attempt to extract long term
steady state (or, indeed, cyclical or chaotic) situations, whiih could potentially 
be used to validate social research, and even be used as a tool to predict the
outcome of policy changes.

We began with a very simple and open-ended system - Agents from groups, then pairs,
then hunt. 
We have since added layers of complexity: more detailed agents and agent interactions 
in terms of the Happiness, Loyalty and Turst attributes and
mecahnisms for leadership through predictors and advice in combination with trust.

We then added the political system, giving agents and groups of agents ideals which 
they strive to emulate and share.
These ideals manifest in terms of the tax rate an agent pays, 
and a group's position is readily modified by the memebers of the group, 
causing a degree of movement about the political compass, allowing us to chart 
how political groups change over time.
Indeed, the manner in which an agent's loyalty and happiness values change in 
response to group movements 
permits us to see how political ideals can influence individual's satisfaction, 
and can cause polarization for or away from the group.
We can imagine this as an agent become disillusioned with politics and changing its ideals.
The concept of emergent leadership that we have shows us how groups fare on the 
vertical politics axis,  and whether one or many leaders is the better strategy 
for hunting and continued survival.

The next stage involved groups loaning food to each other. 
Here, groups in need have a mechanism to avoid collapsing under their own
food deficit, and can request aid. 
These loans were initially designed to mimic the current situation in the EU, 
where the Greek economy is requesting large loans to avoid financial ruin. 
Although the loans we have implemented are simplistic: having a flat interest rate 
and no time penalty for repayment, 
they at least provide a simplistic model for international money lending.

These simulations showed interesting, if predictable, tendencies without
the presence of any warm `fuzzy feeling' from aulturism;
greedy groups went out of their way for food, and less greedy ones were willing
to give it away - even at the expense of their own happiness.

The lack of foresight in these simulations - a fixed amount beign put away for
a rainy day, borrowing when you might not need to, and thereby accumilating
extra interest - means that groups do not perform optimally here.

Parallel to the idea of a political, ``country'' approach to groups and agents, 
we investigated genetic algorithms in an attempt to simulate evolution and
survial of the fittest.
The combination of genertic algorithms and neural networks created an major
counterpoint to the use of primarily fixed strategies.
Even after a short number of cycles, with the agents just learning, we
can see a marked improvement in the fitness for agents that use the
implemented learnnig behaviour.
This, if expanded, could eventually lead to more stable communities.

\section{Evaluation}


With a finished project, we could now become nostalgic and reflect on how we would have 
improved our experience of working as a team. 

To begin with, the most apparent and immediate problem was the size of the team. 
None of us had worked in an environment where 13 people needed to be coordinated and 
managed before and, as a result, we were all reluctant to be a strict leader, resulting in a 
more democratic implementation.
While this wasn't too disruptive for our setup, it did lead to problems with communication 
and no one was holistically aware of everything going on with the project.
Contary to the popular belief in this country, the use of an Alternative Voting system on naming
the project was fair and effective.

One tool that was incredibly helpful, given our large size, was GitHub. 
GitHub enabled all of us to edit the Framework and the Report simultaneously and was 
instrumental in maintaining the workflow as multiple groups approached the codebase
from different angles.

In contrast a tool that was a hinderance was PreSage. 
While it had some useful classes to build on, allowing us to evade many of the complicated 
issues associated with MAS construction, much of the code was poorly documented or unclearly 
implemented. 
As a result, our initial time plan was substantially delayed due to the volume of work that went 
into understanding and ironing out bug in PreSage, much to the detriment of our analysis.

As far as the project output is concerned, one thing we found was our goal to implement loans 
and mimic the EU financial situation was proposed far too late. 
We did not have the time to explore with as much depth as any of us would have wanted and may 
have even re-factored the scope of the project to further investigate genetic algorithms, which we 
had made some real progress with. 
This may have been possible if we were given better notice of deadlines, thus giving us more time 
to plan better targets throughout the project.

Given the issues stated above, we believe we produced a successful project and created a tool with 
great potential. 
Each member of ISE3M was able to shine in their respective specialty, and while some contributions 
were particularly outstanding, everybody played their part in achieving the goals we set out for 
Project MACE.

