\section{Further Work}
\subsection{Thorough Testing and Validation}
In order for a technology to be used in published research, it must be tested and
validated to ensure that the results are caused by properties of your
proposed system, and not by a bug. 
This is also true for tools used to make big, important decisions.
If our software was to show that the best plan of action involved increasing 
taxes for the rich, for example, it would be quickly dismissed, since you 
can't trust something without being absolutely sure there are no bugs.
There are several ways in which such quality assurance can be implemented, from 
low-level unit-testing with JUnit, to high-level testing of simple simulation
cases.

\subsubsection{JUnit}
By using JUnit we could ensure that each of our functions and classes behave
as intended. One problem we encountered was that PreSAGE was not designed with
test-driven development in mind, and is therefore difficult to use with JUnit.
This is perhaps too much to ask from PreSAGE, which is intended to be used
as more of a prototyping solution, rather than the basis of a finished
product\cite{presage1}. Using something such as JADE or AgentBuilder might 
be a better solution, or even creating a bespoke implementation of this multi-agent
system.

\subsection{Varying Environment}
Our society and its environment is currently quite stationary. Once groups have formed,
there is little to cause any significant change in the future of the simulation. This 
predictable and static system means that the idea of international loaning which we have
tried to model is a little unnecessary. Loans exist because there are times when some 
prosper when others are poor, and the fact that this situation may change in the future.
Since our simulation isn't very dynamic, a group that requires loans to survive at one point in time 
will still require loans later on. 

Introducing the idea of famine, disease, aging or injury would make our simulations 
more dynamic, matching more closely the nondeterministic nature of the world we aim to model. 
This could be done by changing how successful hunting is for a certain group. A famine could
mean that hunting results in less food. Disease could be modelled by
having agents disabled for a few cycles. Disease also spreads through a group, so some sort of 
algorithm could be implemented to simulate this behaviour.

\subsection{More Comparison with Ethnographic Studies}
There are many studies in the field of social and cultural anthropology looking at the 
evidence of between-group altruism. Discussion on this topic is mostly intelligent
and well thought-out speculation, which is almost as good as you can get in the science
of behaviour. Recent papers which link their ideas to real-life data seem to be in need
of more examples from the world. This is a problem, since the simple communities which 
exist in isolation of the developed community are increasingly rare and protected. 

Simulation is starting to be used more and more in these fields. If our system was 
verified against the existing data on primitive human societies, then it could be
used as a great source of information for these researchers. 

\subsubsection{The Ache of Paraguay}
The University of New Mexico studied the Ache, `A group of South American 
forager-horticulturists', and noted the altruism shown between families\cite{gurven1}.
This is extremely similar to what we are trying to achieve with our simulations and
so a comparison between the two would be great.

\subsubsection{Liangshan Outlaws}
Another example of data to which our simulations should be compared, is the 
rebellion of the Liangshan outlaws. This is related to the politics side of our simulations,
rather than the loaning aspect. In the Song Dynasty, around 1120AD, the population of 
China was fairly unhappy with the government and their emperor. The emperor then decided
to raise taxes, which is represented in our simulation as a move towards the top-left of the
political compass. This caused a group of unhappy citizens to start a rebellion against 
the government. 

We could simulate this scenario by having the leader of a group move quickly to the top
left of the political compass, and then see whether a group of agents closer to the centre
of the group decide to split off and make their own society - a rebellion. 

After the rebellion had formed, the emperor was forced to lower taxes once again and the two groups
joined back together. This is shown on the political compass below:

\subsubsection{Greater Evolution}

We also could build a lot on the genetic algorithm work, by beginning to model a communtiy
evolving over time.

By recording an agents age, and assuming that most deaths (excluding starvation, which
is dealt with already) can be modelled as a Markov process, we can begin to model
a non-static civilisation.
The next step in this would be the introduction of reproduction, even by modeling
relationships or, again, treating it as a Markov generation process of a group.

This would then allow agents to pass down the things they learn to their child agents,
which might either cause great deviation between groups, or greater homogenity as
one group, depending on what appears to be the optimal strategy.


