\section{Project Plan}
Our project hinged around creating a framework that would allow us to explore
the game environment laid out in the specification. We could then expand this
design to give us some meaningful and applicable results, from which we could draw
some useful information.

The environment would have to manage and regulate a number of players and
control how they are able to interact with each other, as well as the parameters
of the game (in this case, food and groups).
Meanwhile, all aspects of the simulation would need to be monitored, visualised
and analysed while the players are interacting to track the progress of the game.

Players in this game could all be defined by an abstract class which housed
all the functions it uses to interact with the environment.
In this class, algorithms which determine how the player selects from a 
set of food types as well as how it interacts with other agents are housed.
These algorithms are what determines the type of social and economic human the player represents.

Groups themselves will need to have their own behaviour specified in the framework.
They act much like agents, but make decisions based on a combination of strategies 
held by its members. How the group decides between different agents when selecting
behaviour and the way in which agents interact with each other within groups could 
lead to some very interesting results.

Through research, we hope to optimise the variables needed to attempt to mimic
human behaviour in our simulations, using the Multi-Agent System paradigm to
implement our framework.
In this project we hope to investigate the behaviour that emerges from variations in
agent strategies and see what conditions are best suited for a stable population to exist 
within a group or series of groups.

