\section{Motivation}
Computers and technology have affected the fields of science and engineering in an unimaginable way.
Such huge amounts of processing power means that designers of all things
from sky-scrapers to radios, from aeroplanes to physics experiments are now
somewhat reliant on, and benefit greatly from, the use of computer simulations.
Without its application in electronics, for example, the complex integrated
circuits and high frequency PCB designs, which we rely on so much today, would
not have been possible.
Computer simulation ultimately allows us to try
out different ideas without the associated risks of failure; indeed,
simulation can even reveal the best way of achieving a certain goal.

The usefulness of computer simulation naturally encourages us to apply it to new ares.
One of these undersimulated areas is the world of politics and, in particular, the realm of social policy.

\subsection{Politics}
Politics, although remaining fairly traditional in most countries,
is making more and more use of technology: made apparent by the 2008
US Presidential Election.
During the election, the use of video sharing and social networking websites meant that candidates were able to reach a greater proportion of the population in a highly interactive way.
55\% of the USA's adult population used the
internet to keep up to date with the election \cite{pew_camp08}. 

While this is good news for engineers, we think that there is scope for further involvement
of technology in politics.
Arguably more important than the elections, social policy making is one area that 
has yet to make use of computer simulation: to backup or defend it's decisions.
It is however well-placed for the application: the costs of bad decisions are extremely
high and most countries already have substantial data about their population.
What if in the future, policy and political decision making was a much harder 
science, backed with solid, statistical evidence?
Perhaps the many choices which led to the recent economic crisis might have been made differently.
Perhaps election campaigns would be filled with more realistic proposals (verifiable by independent groups).

Of course, simulating the effects of policy decisions is not trivial:
while the physics of an aerofoil and fluids are well known, there is no real
mathematical model of a nation of people.
Different approaches are required and new techniques will be needed.
This project aims to abstract the model of a community, to simulate formation and interaction,
before finally extracting information about the social and economic beliefs of each group.
The sensitivity of the simulation result to various environmental and political factors will also be analysed.
This investigation hopes to show that interesting and useful data can be
generated by computer simulation which can applied to politics.

